\pdfbookmark[1]{Abstract}{Abstract}
\begingroup
\let\clearpage\relax

\chapter*{Abstract}

We propose a method to match similar neighborhoods across different cities.
That is, we give ourselves a measure of similarity between urban regions, as
well as one region in one city. Our goal is to find the region in some other
cities which minimize the distance with the query region. Furthermore, we
seek to do it effienctly, as it is prohivitive to evaluate the distance of
all possible regions.

First, we collect trace of activities in 20 European and American cities from
location aware social platforms \fs{} and \flickr{}. A thorough exploration of
this dataset leads us to describe individual venues by relevant features
including their aggregate activity across time, their visitors and overall
popularity, and the typology of their surrounding.  Then we learned several
measures of venue similarity in a semi-supervised setting and evaluate their
performance on two information retrieval tasks.  After gathering human ground
truth about neighborhoods, we evaluate different metrics between sets of
venues and find out that earth movers distance is the best suited at assessing
neighborhood similarity. Finally, we address the computational efficiency
problem of finding the most similar neighborhood given a query. We devise a
heuristic search strategy and show that it provides results of comparable
quality while being order of magnitude faster. This work has application in
touristic recommendation and urban planning, as it provides a similarity
measure between urban areas.

\endgroup 
\vfill
