%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgments}{acknowledgments}

\begin{flushright}{\slshape    
		I can feel it in my bones \\
		So much left unknown \\
		We continue to grow old \\
		At least I found my gold
    } \\ \medskip
    --- \emph{Gold}, Vinyl Theathre\footnote{From their album of the same
	    name: \href{https://youtu.be/y_hSArYE4kI?t=2m45s}%
	    {\url{youtu.be/y_hSArYE4kI}}.}
\end{flushright}

\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgments}

I am greatly indebted to many people. First to my supervisor, Prof.\@ \myProf,
for suggesting me this topic, providing me thorough and kind guidance for more
than six months, and for compensating my usual lack of enthusiasm with his.
Coming second only by alphabetical order, I also want to offer my gratitude to
my advisor, Dr.\@ \mySupervisor for his help and his fine remarks concerning my
writing. This research wad conducted while I was part of the
Data Mining Group\footnote{\href{http://research.ics.aalto.fi/dmg/}%
{\url{research.ics.aalto.fi/dmg/}}} and I am thankful for having met such
nice and bright people (and for having eaten many different kinds of cake
during the meetings). Actually, I may as well thank all the people I have
worked with at \myUni, because it was a real pleasure. Even more broadly, this
time in Finland was a delight, made possible by the impressive, pristine nature
as as much by the kindness of people living there.

In addition to these talented and supportive people, this work would not have
been possible if not for many great open-source softwares. Yet because it would
feel weird to thanks them in the same place, I relegate them in \autoref{chap:ack}.

On a personal level, I would first like to thank the members of my family for
their unconditional support. I have also heavily relied on friends for their
knowledge on Paris; yet neither Camille Autran, Oliver Braud nor Aloïs Guillopé
have ever expressed any irritation (at least openly).  As I am finishing the
redaction of this manuscript, I have to acknowledge that, however frequent and
unexpected, the interruptions of Kiran Garimella were probably beneficial in
the long term. Finally, the outcome would certainly have been different without
the influence of Sanja Šćepanović; both objectively---for giving me the Twitter
API key used to collect my dataset--- and subjectively---for so many reasons that
it would be pointless to try to condense them in a few sentences.

\endgroup
