\chapter{Introduction}
\label{ch:introduction}

\section{Motivation}

More and more people are living in cities\footnote{According to an
\href{http://esa.un.org/unup/pdf/WUP2011_Highlights.pdf}{UN report}
\autocite{UNreport12}, \enquote{the population living in urban areas is
projected to [pass] from 3.6 billion in 2011 to 6.3 billion in 2050.}}. This
simple observation leads to two questions: how to help urban dwellers make
informed everyday decisions and how to understand these large and complex
systems. Fortunately, now is a good time to tackle these issues. Indeed, thanks
to social networks and mobile devices, we know where and when people are
active within cities \autocite{SpatialComputing12}. We seize this opportunity
to devised a similarity measure between urban areas. First we motivate the
need for such a measure through a typical use case:

\begin{quote}
Let us say you have lived in a city for the last years. During this time,
you have acquired urban knowledge that you can leverage to find relevant
locations where to perform various tasks. In simpler words, whether you want
to buy milk, listen to loud music or exhibit your athletic skills, you know
where to go. Yet life is full of surprises and you may be spending a few
days in a new town. Fair enough, but you do not want to renounce to your
wide range of outside activities. This is where our application comes in
handy. You select a location or an area in your familiar city and it shows
you a place or a zone sharing similar characteristics in your surrounding.
Thus you can boldly venture into distant shores, reassured that a part of
your home will always travels with you.
\end{quote}

This short illustration gives an intuitive definition of the problem we are
trying to solve. Namely, an user picks a small part of a city and we represent
it by a bag of all venues it contains. These venues are associated with some
features and we want to find, efficiently, a set of venues that shares similar
characteristics. Yet for this result to be meaningful, we add the constraint
that the venues must delineate a neighborhood, that is a small and compact
subset of the whole city.

In the next section, we will give a more precise problem statement. Before
that, notice that although we define it in terms of cities and venues, it can
be generalized to other settings. All we need is a set of disconnected metric
spaces\footnote{Here two dimensional plane underlying the cities.}, points
lying in those spaces and described by some features\footnote{Here the venues
described by their activity.} and a set of latent high-level characteristics
associated with set of points\footnote{For instance here, \enquote{nightlife
neighborhood} or \enquote{touristic hotspot}.}. Here are some examples that
can be modeled under this framework:
\begin{itemize}
	\item The social graph of students in several universities. The metric
		is a distance in the graph and featured points are students.
		Picking some of them, we posit that they are close because
		they share the same degree program or some other demographic.
		We want to know if the same group exists elsewhere.
	\item Graph of twitter users in different cities or countries. They
		are described by the topic distribution of their tweets. We
		ask whether some community of interest exist in several places
		in the world.
	\item The set of all books ever written, grouped by centuries and
		characterised by their style and main themes. Choosing all
		pieces written during the Enlightenment, it would tell if
		there was a similar movement in the twentieth century.
\end{itemize}
Even though these examples are not all relevant, they provide additional
motivation to solve the problem at hand.
